---
title: "Linear regression"
author: "Sowmiya"
date: "21/11/2019"
output:
  html_document: default
---

1. Introduction to Linear Regression:

  Linear regression is one of the most commonly used predictive modelling techniques. The aim of linear regression is to find a mathematical equation for a continuous response variable Y as a function of one or more X variable(s). So that you can use this regression model to predict the Y when only the X is known.

This mathematical equation can be generalised as follows:

$$Y = \beta_{1} + \beta_{2} X + \epsilon$$
where, β1 is the intercept and β2 is the slope.

Collectively, they are called regression coefficients and ϵ is the error term, the part of Y the regression model is unable to explain.

2. Example Problem
(1)For this analysis, we will use the marketing dataset.

#Description
A data frame containing the impact of three advertising medias (youtube, facebook and newspaper) on sales. Data are the advertising budget in thousands of dollars along with the sales.
it consists of 200 observations(rows) and 4 variables (columns).

```{r}
library(datarium)
#data("marketing", package = "datarium")
data("marketing")
View(marketing)
```

(2)Lets print out the first six observations here.
```{r}
head(marketing)
```

(3)To check the structure of the data:
```{r}
str(marketing)
```

(4)what is the maximum and minimum of these data values?

```{r}
summary(marketing)
```


3. Graphical Analysis:

The aim of this exercise is to build a simple regression model that you can use to predict future sales on the basis of advertising budget spent on youtube.

```{r}
library(ggplot2)
ggplot(marketing,mapping = aes(youtube,sales))+geom_point()
```

The scatter plot along with the smoothing line above suggests a linear and positive relationship between the ‘sales’ and ‘youtube’.

4. What is Correlation Analysis?
Correlation is a statistical measure that shows the degree of linear dependence between two variables.

Correlation can take values between -1 to +1.

If one variables consistently increases with increasing value of the other, then they have a strong positive correlation (value close to +1).

Similarly, if one consistently decreases when the other increase, they have a strong negative correlation (value close to -1).

A value closer to 0 suggests a weak relationship between the variables.
```{r}
cor(marketing$sales,marketing$youtube)
```
In our example, the correlation coefficient is large enough, so we can continue by building a linear model of y as a function of x.

5. Building the Linear Regression Model:



 function used for building linear models is lm().
```{r}
model <- lm(sales ~ youtube, data = marketing)
model
```
The linear model equation can be written as follow: sales = b0 + b1 * youtube

5.1.Interpretation

From the output above:

the estimated regression line equation can be written as follow: sales = 8.44 + 0.048*youtube

the intercept (b0) is 8.44. It can be interpreted as the predicted sales unit for a zero youtube advertising budget. Recall that, we are operating in units of thousand dollars. This means that, for a youtube advertising budget equal zero, we can expect a sale of 8.44 *1000 = 8440 dollars.

the regression beta coefficient for the variable youtube (b1), also known as the slope, is 0.048. This means that, for a youtube advertising budget equal to 1000 dollars, we can expect an increase of 48 units (0.048*1000) in sales. That is, sales = 8.44 + 0.048*1000 = 56.44 units. As we are operating in units of thousand dollars, this represents a sale of 56440 dollars.


5.2.Regression line
To add the regression line onto the scatter plot, you can use the function stat_smooth() [ggplot2]. 
```{r}
ggplot(marketing, aes(youtube, sales)) + geom_point() +   stat_smooth(method = lm)
```
5.3 Summary

```{r}
summary(model)
```
Residual standard error (RSE), R-squared (R2) and the F-statistic are metrics that are used to check how well the model fits to our data.
In our example, both the p-values for the intercept and the predictor variable are highly significant, so we can reject the null hypothesis and accept the alternative hypothesis, which means that there is a significant association between the predictor and the outcome variables.

5.4Summary

After computing a regression model, a first step is to check whether, at least, one predictor is significantly associated with outcome variables.

If one or more predictors are significant, the second step is to assess how well the model fits the data by inspecting the Residuals Standard Error (RSE), the R^2 value and the F-statistics. These metrics give the overall quality of the model.
```{r}
model2=lm(sales ~ youtube*facebook, data = marketing)
summary(model2)
```

RSE: Closer to zero the better
R-Squared: Higher the better
F-statistic: Higher the better

